Manifold Clustering in the Setting of Generalized Random Dot Product Graphs

### 2023-05-22 sdss-2023/poster-2.Rmd
alternative poster

---
title: Manifold Clustering in the Setting of Generalized Random Dot Product Graphs
author:
  - name: John Koo
    affil: 1
  - name: Minh Tang
    affil: 2
  - name: Michael W. Trosset
    affil: 1
affiliation:
  - num: 1
    address: Indiana University
  - num: 2
    address: North Carolina State University
title_textsize: "56pt"
author_textsize: "32pt"
affiliation_textsize: "8pt"
sectitle_textsize: "36pt"
sectitle2_textsize: "36pt"
body_textsize: "32pt"
column_numbers: 4
poster_height: "20.5in"
poster_width: "36.5in"
column_margins: "0.1in"
primary_colour: "#990000"
secondary_colour: "#000000"
accent_colour: "#990000"
titlebox_borderwidth: "0.1cm"
titlebox_bordercol: "#000000"
title_textcol: "#ffffff"
author_textcol: "#ffffff"
sectitle2_textcol: "#990000"
sectitle_borderwidth: "0mm"
font_family: "Times New Roman"
logoleft_name: poster_files/trident_medium.png
output: 
  posterdown::posterdown_html:
    self_contained: true
    keep_tex: true
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{mathtools}
- \usepackage{natbib}
- \usepackage[linesnumbered,ruled,vlined]{algorithm2e} 
- \setcitestyle{numbers,square,comma}
- \usepackage{verbatim}
- \usepackage{amsthm}
- \usepackage{comment}
- \usepackage{graphicx}
- \setbeamertemplate{itemize items}[circle]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      comment = NA, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.align = 'center',
                      fig.lp = '')
import::from(magrittr, `%>%`)
library(ggplot2)
library(ggraph)
source('~/dev/pabm-grdpg/functions.R')
source('~/dev/manifold-block-models/functions.R')
```

@@

# Generalized Random Dot Product Graphs

The *generalized random dot product graph* is a random graph model in which each vertex $v_i$ has a corresponding hidden vector $x_i \in \mathbb{R}^{p+q}$ and each edge probability is the indefinite inner product of the corresponding pair of hidden vectors, i.e., $P_{ij} = x_i^\top I_{p, q} x_j$, $I_{p,q} = \Bigl[\begin{smallmatrix} I_{p} & 0 \\ 0 & - I_{q} \end{smallmatrix} \Bigr]$

## Adjacency Spectral Embedding
Approximate $A$ by spectral decomposition $A \approx V_{p, q} \Lambda_{p, q} V_{p, q}^\top$. 
The subscript $p, q$ denotes the $p$ most positive and $q$ most negative eigenvalues and corresponding eigenvectors. 
Each $\hat{x}_i$, the $i^{th}$ row of $\hat{X} = V_{p, q} |\Lambda_{p, q}|^{1/2},$ estimates the relative position of its corresponding latent vector $x_i$, up to an indefinite orthogonal transformation.

**Theorem** (Rubin-Delanchy et al. 2022): $\max_i \| \hat{x}_i - Q_n x_i \| = O_P \Big( \frac{\log^c n}{n^{1/2}} \Big)$ for some $Q_n \in \mathbb{O}(p, q)$.

```{r, cache = TRUE}
n1 <- 2 ** 5
n2 <- 2 ** 5
n <- n1 + n2
z <- c(rep(1, n1), rep(2, n2))
u1 <- runif(n1)
u2 <- runif(n2)
x1 <- cos(pi / 3 * u1)
y1 <- sin(pi / 3 * u1)
x2 <- 1 + cos(pi / 3 * u2 + pi)
y2 <- 1 + sin(pi / 3 * u2 + pi)

data.matrix <- cbind(c(x1, x2), c(y1, y2))
P <- data.matrix %*% diag(c(1, 1)) %*% t(data.matrix)
A <- draw.graph(P)
A.graph <- tidygraph::as_tbl_graph(A, directed = FALSE)

Xhat <- embedding(A, 2, 0)
Xhat[, 1] <- -Xhat[, 1]
```

```{r, fig.height = 2.25, fig.width = 6, out.width = '100%'}
latent.config.plot <- ggplot() + 
  geom_point(aes(x = data.matrix[, 1], y = data.matrix[, 2], 
                 colour = factor(z))) + 
  # coord_fixed() + 
  theme_bw() + 
  theme(legend.position = 'none') + 
  labs(x = NULL, y = NULL, colour = NULL, title = 'Latent Vectors') + 
  scale_colour_brewer(palette = 'Set1') +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

graph.plot <- ggraph(A, layout = 'stress') + 
  geom_edge_link(alpha = 1 / sqrt(n) / 2) + 
  geom_node_point(aes(colour = factor(z)),
                  show.legend = FALSE) + 
  labs(colour = NULL, 
       title = 'GRDPG') + 
  # theme_graph() + 
  theme_void() + 
  scale_colour_brewer(palette = 'Set1')

ase.plot <- ggplot() + 
  geom_point(aes(x = Xhat[, 1], y = Xhat[, 2],
                 colour = factor(z))) + 
  # coord_fixed() + 
  theme_bw() + 
  theme(legend.position = 'none') + 
  labs(x = NULL, y = NULL, colour = NULL, title = 'ASE') + 
  scale_colour_brewer(palette = 'Set1') +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

gridExtra::grid.arrange(latent.config.plot, graph.plot, ase.plot, nrow = 1)
```

@@

SBM, DCBM, and PABM are GRDPGs in which the communities correspond to linear structures in the latent space.

```{r, cache = TRUE, fig.width = 5, fig.height = 2.4, out.width = '100%'}
n <- 64
n1 <- n / 2
n2 <- n / 2
z <- c(rep(1, n1), rep(2, n2))
p <- 1/2
q <- 1/2
r <- 1/8
P <- matrix(r, nrow = n, ncol = n)
P[seq(n1), seq(n1)] <- p
P[seq(n1 + 1, n), seq(n1 + 1, n)] <- q
X <- embedding(P, 2, 0)
A <- draw.graph(P)
Xhat <- embedding(A, 2, 0)
A.graph <- tidygraph::as_tbl_graph(A, directed = FALSE)

@@

```{r, cache = TRUE, fig.width = 5, fig.height = 2.4, out.width = '100%'}
n <- 128
n1 <- n / 2
n2 <- n / 2
z <- c(rep(1, n1), rep(2, n2))
p <- 1/2
q <- 1/2
r <- 1/8
P <- matrix(r, nrow = n, ncol = n)
P[seq(n1), seq(n1)] <- p
P[seq(n1 + 1, n), seq(n1 + 1, n)] <- q
omega <- rbeta(n, 2, 1)
P <- P * (omega %*% t(omega))
X <- embedding(P, 2, 0)
A <- draw.graph(P)
Xhat <- embedding(A, 2, 0)
Xhat <- Xhat
A.graph <- tidygraph::as_tbl_graph(A, directed = FALSE)

@@

```{r, cache = TRUE, fig.width = 5, fig.height = 2.4, out.width = '100%'}
n <- 64
Pz <- generate.P.beta(n)
P <- Pz$P
z <- Pz$clustering
X <- embedding(P, 3, 1)
A <- draw.graph(P)
Xhat <- embedding(A, 3, 1)
# Xhat[, 2] <- -Xhat[, 2]
A.graph <- tidygraph::as_tbl_graph(A, directed = FALSE)

@@

graph.r <- generate.graph(newrdat, vdf.right)
A.r <- as.matrix(igraph::as_adjacency_matrix(graph.r$g, type = 'both'))
z.r <- as.numeric(graph.r$vdf$type)
n.r <- length(z.r)
A.r <- sign(A.r + t(A.r))
diag(A.r) <- 0
graph.r <- ggraph(A.r, layout = 'stress') + 
  geom_edge_link(alpha = 1 / sqrt(n.r) / 2) + 
  geom_node_point(aes(colour = factor(z.r)), 
                  show.legend = FALSE) + 
  labs(colour = NULL) + 
  theme_void() + 
  scale_colour_brewer(palette = 'Set1')

graph.l <- generate.graph(newldat, vdf.left)
A.l <- as.matrix(igraph::as_adjacency_matrix(graph.l$g, type = 'both'))
z.l <- as.numeric(graph.l$vdf$type)
n.l <- length(z.l)
A.l <- sign(A.l + t(A.l))
diag(A.l) <- 0
graph.l <- ggraph(A.l, layout = 'stress') + 
  geom_edge_link(alpha = 1 / sqrt(n.l) / 2) + 
  geom_node_point(aes(colour = factor(z.l)), 
                  show.legend = FALSE) + 
  labs(colour = NULL) + 
  theme_void() + 
  scale_colour_brewer(palette = 'Set1')

@@

```{r mbconnectome-ase, fig.height = 3.75, fig.width = 7, out.width = '100%', cache = TRUE}
Xhat.l <- embedding(A.l, 2, 1)
ase.l <- ggplot() + 
  geom_point(aes(x = Xhat.l[, 1], y = Xhat.l[, 2],
                 colour = factor(z.l))) + 
  # coord_fixed(.5) +
  theme_bw() + 
  theme(legend.position = 'none') +
  scale_colour_brewer(palette = 'Set1') + 
  labs(x = NULL, y = NULL, colour = NULL) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

@@

Let $p, q \geq 0$, $d = p + q \geq 1$, $1 \leq r < d$, $K \geq 2$, and $n > K$ be integers. 
Define manifolds $\mathcal{M}_1, ..., \mathcal{M}_K \in \mathcal{X}$ for $\mathcal{X} = \{x, y \in \mathbb{R}^d : x^\top I_{p,q} y \in [0, 1]\}$ each by continuous function $g_k : [0, 1]^r \to \mathcal{X}$. 
Define probability distribution $F$ with support $[0, 1]^r$. 
Then the following mixture model is a *manifold block model*:

@@

1. Compute $X$, the ASE of $A$ using the $p$ most positive and $q$ most negative eigenvalues and their corresponding eigenvectors.
2. Initialize community labels $z_1, ..., z_n$.
3. While change in $\sum_k \sum_{i \in C_k} \|x_i - g_k(t_i)\|^2$ is less than $\epsilon$: 
    i. For $k = 1, ..., K$:
        a. Define $X_k$ as the rows of $X$ for which $z_i = k$.
        b. Fit curve $g_k$ and positions $t_{k_i}$ to $X_k$ by minimizing $\sum_{k_i} \|x_{k_i} - g_k(t_{k_i})\|^2$.
    ii. For $k = 1, ..., K$: 
        a. Assign $z_i \leftarrow \arg\min_\ell \|x_i - g_\ell(t_i)\|^2$.

```{r mbconnectome-kcurves, fig.height = 2, fig.width = 8, cache = TRUE, out.width = '100%'}
set.seed(123456)

@@

>>>>

---
title: Manifold Clustering in the Setting of Generalized Random Dot Product Graphs
author:
  - name: John Koo
    affil: 1
  - name: Minh Tang
    affil: 2
  - name: Michael W. Trosset
    affil: 1
affiliation:
  - num: 1
    address: Indiana University
  - num: 2
    address: North Carolina State University
title_textsize: "48pt"
author_textsize: "32pt"
affiliation_textsize: "8pt"
sectitle_textsize: "34pt"
sectitle2_textsize: "34pt"
body_textsize: "32pt"
column_numbers: 4
poster_height: "20.5in"
poster_width: "36.5in"
column_margins: "0.01in"
primary_colour: "#990000"
secondary_colour: "#000000"
accent_colour: "#990000"
titlebox_borderwidth: "0.01cm"
titlebox_bordercol: "#000000"
title_textcol: "#ffffff"
author_textcol: "#ffffff"
sectitle2_textcol: "#990000"
sectitle_borderwidth: "0mm"
font_family: "Latin Modern Math"
logoleft_name: poster_files/trident_medium.png
output: 
  posterdown::posterdown_html:
    self_contained: true
    keep_tex: true
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{mathtools}
- \usepackage{natbib}
- \usepackage[linesnumbered,ruled,vlined]{algorithm2e} 
- \setcitestyle{numbers,square,comma}
- \usepackage{verbatim}
- \usepackage{amsthm}
- \usepackage{comment}
- \usepackage{graphicx}
- \setbeamertemplate{itemize items}[circle]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      comment = NA, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.align = 'center',
                      fig.lp = '')
import::from(magrittr, `%>%`)
library(ggplot2)
library(ggraph)
source('~/dev/pabm-grdpg/functions.R')
source('~/dev/manifold-block-models/functions.R')

doMC::registerDoMC(8)
```

@@

@@

SBM, DCBM, and PABM are generalized random dot product graphs in which the communities correspond to linear structures in the latent space.

```{r, cache = TRUE, fig.width = 5, fig.height = 2.25, out.width = '100%'}
set.seed(314159)

n <- 64
n1 <- n / 2
n2 <- n / 2
z <- c(rep(1, n1), rep(2, n2))
p <- 1/2
q <- 1/2
r <- 1/8
P <- matrix(r, nrow = n, ncol = n)
P[seq(n1), seq(n1)] <- p
P[seq(n1 + 1, n), seq(n1 + 1, n)] <- q
X <- embedding(P, 2, 0)
A <- draw.graph(P)
Xhat <- embedding(A, 2, 0)
Xhat <- -Xhat
A.graph <- tidygraph::as_tbl_graph(A, directed = FALSE)

@@

```{r, cache = TRUE, fig.width = 5, fig.height = 2.25, out.width = '100%'}
set.seed(314159)

n <- 128
n1 <- n / 2
n2 <- n / 2
z <- c(rep(1, n1), rep(2, n2))
p <- 1/2
q <- 1/2
r <- 1/8
P <- matrix(r, nrow = n, ncol = n)
P[seq(n1), seq(n1)] <- p
P[seq(n1 + 1, n), seq(n1 + 1, n)] <- q
omega <- rbeta(n, 2, 1)
P <- P * (omega %*% t(omega))
X <- embedding(P, 2, 0)
A <- draw.graph(P)
Xhat <- embedding(A, 2, 0)
Xhat <- Xhat
A.graph <- tidygraph::as_tbl_graph(A, directed = FALSE)

@@

```{r, cache = TRUE, fig.width = 5, fig.height = 2.25, out.width = '100%'}
set.seed(314159)

n <- 64
Pz <- generate.P.beta(n)
P <- Pz$P
z <- Pz$clustering
X <- embedding(P, 3, 1)
A <- draw.graph(P)
Xhat <- embedding(A, 3, 1)
# Xhat[, 2] <- -Xhat[, 2]
A.graph <- tidygraph::as_tbl_graph(A, directed = FALSE)

@@

graph.r <- generate.graph(newrdat, vdf.right)
A.r <- as.matrix(igraph::as_adjacency_matrix(graph.r$g, type = 'both'))
z.r <- as.numeric(graph.r$vdf$type)
n.r <- length(z.r)
A.r <- sign(A.r + t(A.r))
diag(A.r) <- 0
A.r.graph <- tidygraph::as_tbl_graph(unname(A.r), directed = FALSE)
graph.r <- ggraph(A.r.graph, layout = 'stress') + 
  geom_edge_link(alpha = 1 / sqrt(n.r) / 2) + 
  geom_node_point(aes(colour = factor(z.r)), 
                  show.legend = FALSE) + 
  labs(colour = NULL) + 
  theme_void() + 
  scale_colour_brewer(palette = 'Set1')

graph.l <- generate.graph(newldat, vdf.left)
A.l <- as.matrix(igraph::as_adjacency_matrix(graph.l$g, type = 'both'))
z.l <- as.numeric(graph.l$vdf$type)
n.l <- length(z.l)
A.l <- sign(A.l + t(A.l))
diag(A.l) <- 0
A.l.graph <- tidygraph::as_tbl_graph(unname(A.l), directed = FALSE)
graph.l <- ggraph(A.l.graph, layout = 'stress') + 
  geom_edge_link(alpha = 1 / sqrt(n.l) / 2) + 
  geom_node_point(aes(colour = factor(z.l)), 
                  show.legend = FALSE) + 
  labs(colour = NULL) + 
  theme_void() + 
  scale_colour_brewer(palette = 'Set1')

@@

```{r mbconnectome-ase, fig.height = 5, fig.width = 7, out.width = '75%', cache = TRUE}
Xhat.l <- embedding(A.l, 2, 1)
ase.l <- ggplot() + 
  geom_point(aes(x = Xhat.l[, 1], y = Xhat.l[, 2],
                 colour = factor(z.l))) + 
  # coord_fixed(.5) +
  theme_bw() + 
  theme(legend.position = 'none') +
  scale_colour_brewer(palette = 'Set1') + 
  labs(x = NULL, y = NULL, colour = NULL) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

@@

Let $p, q \geq 0$, $d = p + q \geq 1$, $1 \geq r < d$, $K \geq 2$, and $n > K$ be integers. 
Let $\mathcal{X} = \{x, y \in \mathbb{R}^d : x^\top I_{p,q} y \in [0, 1]\}$ and define manifolds $\mathcal{M}_1, ..., \mathcal{M}_K \subset \mathcal{X}$ each by continuous function $g_k : [0, 1]^r \to \mathcal{X}$. 
Define probability distribution $F$ with support $[0, 1]^r$. 
Then the following mixture model is a *manifold block model*:

@@

1. Compute $X$, the ASE of $A$ using the $p$ most positive and $q$ most negative eigenvalues and their corresponding eigenvectors.
2. Initialize community labels $z_1, ..., z_n$.
3. While change in the loss function $L = \sum_k \sum_{i \in C_k} \|x_i - g_k(t_i)\|^2$ is less than $\epsilon$: 
    i. For $k = 1, ..., K$:
        a. Define $X_k$ as the rows of $X$ for which $z_i = k$.
        b. Fit curve $g_k$ and positions $t_{k_i}$ by minimizing $\sum_{k_i} \|x_{k_i} - g_k(t_{k_i})\|^2$.
    ii. For $k = 1, ..., K$: 
        a. Assign $z_i \leftarrow \arg\min_\ell \|x_i - g_\ell(t_i)\|^2$.

```{r mbconnectome-kcurves, fig.height = 2, fig.width = 6, cache = TRUE, out.width = '67%'}
set.seed(123456)

@@

**Theorem**. 
Let an MBM be such that the manifolds are described as polynomial curves of order $R$. 
Suppose that for each community $k$, we have labels for at least $R + 1$ vertices. 
Then $K$-curves clustering outputs estimates such that  
$$L(\hat{z}_1, ..., \hat{z}_n, \hat{g}_1, ..., \hat{g}_K; X) \stackrel{p}{\to} 0.$$

# Simulation

Latent vectors were drawn uniformly on three intersecting quadratic curves in $\mathbb{R}^3$ (left) to construct a GRDPG (middle). 
Curves were then fitted to the ASE (right) and embedding vectors were assigned labels based on proximity to the curves.

```{r three-curves, cache = TRUE, fig.height = 2, fig.width = 6, out.width = '100%'}
set.seed(314159)
par(mfrow = c(1, 3))

n <- 512

p.list <- list(matrix(c(0, 1, 0, 
                        0, 0, 1,
                        0, 0, 0),
                      nrow = 3, ncol = 3),
               matrix(c(0, 0, 0, 
                        0, 0, 1,
                        0, 1, 0),
                      nrow = 3, ncol = 3),
               matrix(c(0, 1, 0, 
                        0, 0, 1,
                        0, 1, 0),
                      nrow = 3, ncol = 3))

K <- length(p.list)

z <- sample(seq(K), n, replace = TRUE)
z <- sort(z)

t <- runif(n)

X <- lapply(seq(K), function(k) {
  bezier.curve(t[z == k], 
               p.list[[k]], 
               intercept = TRUE)
}) %>% 
  do.call('rbind', .)

p <- ncol(X)
q <- 0

P <- grdpg.edge.prob.matrix(X, p, q)
A <- draw.graph(P)
Xhat <- embedding(A, p, q)

scatterplot3d::scatterplot3d(X[, 1], X[, 2], X[, 3],
                             color = z + 1, 
                             mar = c(0, 0, 0, 0),
                             xlab = NA, ylab = NA, zlab = NA,
                             # pch = '.', 
                             asp = 1,
                             tick.marks = FALSE)

qgraph::qgraph(A, 
               groups = factor(z), 
               legend = FALSE,
               mar = c(0, 0, 0, 0))

scatterplot3d::scatterplot3d(Xhat[, 1], Xhat[, 2], Xhat[, 3], 
                             color = z + 1, 
                             mar = c(0, 0, 0, 0),
                             xlab = NA, ylab = NA, zlab = NA, 
                             # pch = '.', 
                             asp = 1,
                             # angle = 40,
                             tick.marks = FALSE)
```

```{r sim-curves-3, fig.height = 3, fig.width = 8, out.width = '100%', cache = TRUE}
n.vec <- 2 ^ c(7, 8, 9, 10, 11)
nsamp.vec <- c(0, 4, 8)

clustering.df <- readr::read_csv('~/dev/manifold-block-models/simulations/balanced-3/balanced-3.csv')

clust.summary.df <- clustering.df %>% 
  dplyr::group_by(n, nsamp) %>% 
  dplyr::summarise(
    med.count = median(error.count),
    first.q.count = quantile(error.count, .25),
    third.q.count = quantile(error.count, .75),
    med.rate = median(error.rate),
    first.q.rate = quantile(error.rate, .25),
    third.q.rate = quantile(error.rate, .75)
  ) %>% 
  dplyr::ungroup()

ggplot(clust.summary.df) + 
  theme_bw() + 
  theme(text = element_text(size = 10)) + 
  scale_y_log10() +
  scale_x_log10(breaks = n.vec) +
  labs(y = 'community detection error rate',
       x = 'n',
       colour = 'known labels per community', 
       shape = NULL) + 
  geom_line(aes(x = n, y = med.rate, colour = factor(nsamp))) + 
  geom_point(aes(x = n, y = med.rate, colour = factor(nsamp))) + 
  geom_errorbar(aes(x = n, 
                    ymin = first.q.rate, ymax = third.q.rate, 
                    colour = factor(nsamp)),
                width = .125) + 
  theme(legend.position = 'bottom') + 
  scale_colour_brewer(palette = 'Set1')
```

### 2023-05-22 sdss-2023/poster.Rmd
alternative poster

---
title: Manifold Clustering in the Setting of Generalized Random Dot Product Graphs
author:
  - name: John Koo
    affil: 1
  - name: Minh Tang
    affil: 2
  - name: Michael W. Trosset
    affil: 1
affiliation:
  - num: 1
    address: Indiana University
  - num: 2
    address: North Carolina State University
title_textsize: "56pt"
author_textsize: "32pt"
affiliation_textsize: "8pt"
sectitle_textsize: "36pt"
sectitle2_textsize: "36pt"
body_textsize: "32pt"
column_numbers: 4
poster_height: "20.5in"
poster_width: "36.5in"
column_margins: "0.1in"
primary_colour: "#990000"
secondary_colour: "#000000"
accent_colour: "#990000"
titlebox_borderwidth: "0.1cm"
titlebox_bordercol: "#000000"
title_textcol: "#ffffff"
author_textcol: "#ffffff"
sectitle2_textcol: "#990000"
sectitle_borderwidth: "0mm"
font_family: "Times New Roman"
logoleft_name: poster_files/trident_medium.png
output: 
  posterdown::posterdown_html:
    self_contained: true
    keep_tex: true
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{mathtools}
- \usepackage{natbib}
- \usepackage[linesnumbered,ruled,vlined]{algorithm2e} 
- \setcitestyle{numbers,square,comma}
- \usepackage{verbatim}
- \usepackage{amsthm}
- \usepackage{comment}
- \usepackage{graphicx}
- \setbeamertemplate{itemize items}[circle]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      comment = NA, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.align = 'center',
                      fig.lp = '')
import::from(magrittr, `%>%`)
library(ggplot2)
library(ggraph)
source('~/dev/pabm-grdpg/functions.R')
source('~/dev/manifold-block-models/functions.R')
```

\newcommand{\diag}{\text{diag}}
\newcommand{\tr}{\text{Tr}}
\newcommand{\blockdiag}{\text{blockdiag}}
\newcommand{\indep}{\stackrel{\text{ind}}{\sim}}
\newcommand{\iid}{\stackrel{\text{iid}}{\sim}}
\newcommand{\Bernoulli}{\text{Bernoulli}}
\newcommand{\Betadist}{\text{Beta}}
\newcommand{\BG}{\text{BernoulliGraph}}
\newcommand{\Categorical}{\text{Cat}}
\newcommand{\Uniform}{\text{Uniform}}
\newcommand{\RDPG}{\text{RDPG}}
\newcommand{\GRDPG}{\text{GRDPG}}
\newcommand{\PABM}{\text{PABM}}
\newtheorem{theorem}{Theorem}

>>>>

---
title: Manifold Clustering in the Setting of Generalized Random Dot Product Graphs
author:
  - name: John Koo
    affil: 1
  - name: Minh Tang
    affil: 2
  - name: Michael W. Trosset
    affil: 1
affiliation:
  - num: 1
    address: Indiana University
  - num: 2
    address: North Carolina State University
title_textsize: "52pt"
author_textsize: "32pt"
affiliation_textsize: "8pt"
sectitle_textsize: "34pt"
sectitle2_textsize: "34pt"
body_textsize: "32pt"
column_numbers: 4
poster_height: "20.5in"
poster_width: "36.5in"
column_margins: "0.05in"
primary_colour: "#990000"
secondary_colour: "#000000"
accent_colour: "#990000"
titlebox_borderwidth: "0.1cm"
titlebox_bordercol: "#000000"
title_textcol: "#ffffff"
author_textcol: "#ffffff"
sectitle2_textcol: "#990000"
sectitle_borderwidth: "0mm"
font_family: "Latin Modern Math"
logoleft_name: poster_files/trident_medium.png
output: 
  posterdown::posterdown_html:
    self_contained: true
    keep_tex: true
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{mathtools}
- \usepackage{natbib}
- \usepackage[linesnumbered,ruled,vlined]{algorithm2e} 
- \setcitestyle{numbers,square,comma}
- \usepackage{verbatim}
- \usepackage{amsthm}
- \usepackage{comment}
- \usepackage{graphicx}
- \setbeamertemplate{itemize items}[circle]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      comment = NA, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.align = 'center',
                      fig.lp = '')
import::from(magrittr, `%>%`)
library(ggplot2)
library(ggraph)
source('~/dev/pabm-grdpg/functions.R')
source('~/dev/manifold-block-models/functions.R')
doMC::registerDoMC(8)
```

\singlespacing
\newcommand{\diag}{\text{diag}}
\newcommand{\tr}{\text{Tr}}
\newcommand{\blockdiag}{\text{blockdiag}}
\newcommand{\indep}{\stackrel{\text{ind}}{\sim}}
\newcommand{\iid}{\stackrel{\text{iid}}{\sim}}
\newcommand{\Bernoulli}{\text{Bernoulli}}
\newcommand{\Betadist}{\text{Beta}}
\newcommand{\BG}{\text{BernoulliGraph}}
\newcommand{\Categorical}{\text{Cat}}
\newcommand{\Uniform}{\text{Uniform}}
\newcommand{\RDPG}{\text{RDPG}}
\newcommand{\GRDPG}{\text{GRDPG}}
\newcommand{\PABM}{\text{PABM}}
\newtheorem{theorem}{Theorem}
